\chapter{Conclusion and Outlook} \label{chap:summary}
%
%Outlook:
% - To improve the mesh characteristics (to avoid distorted elements)
%
%Summary:

This thesis presents a novel passive mechanism for achieving wing twist morphing by means of modifying the bending-twist coupling of wing structures. The system incorporates a variable-stiffness spar in the wing-box that comprises a lattice of chiral elements. In the ligaments of these elements, elastic instabilities are intentionally induced and thus the effective shear modulus of the adaptive spar is modified. This phenomena provokes the wing-box section shear centre shifting and the consequent modification in wing-box torsional stiffness. This induces a wing-box twist adaptation that has been passively activated exploiting local elastic instabilities.

An analytical model of the wing-box is developed using an ideal beam configuration with variable shear modulus in one of the webs. The effect of variations of this magnitude on the torsional stiffness, the flexural stiffness, the shear centre position and the bending and twisting deformations of the wing-box are studied. Also, the effect of variations of the geometry in these magnitudes is analysed. Results show that, once the buckling-induced reduction in shear modulus in the spar is activated, the reduction in flexural stiffness for the wing-box is negligible compared with the reduction in torsional stiffness. 

A computational model of the simplified wing-box is built next. It is designed in a fully parameterized format using Python scripting. This model is constituted of a wing-box in C-profile, a lattice of chiral elements and a number of ribs that provide additional transversal stiffness and avoid local deformations in the wing-box skin. Different design options are considered, such as variations in the geometry, the load, the mesh and the number of ribs. An analysis of this model is performed in order to obtain a baseline configuration to posteriorly execute parametric studies. One of the aspects considered is the modeling of the lattice nodes rigid body behavior. Results shows that the most suitable modeling approach is to add an additional rigid part to provide supplementary stiffness. The addition of ribs in the middle of wing-box length is necessary to provide additional stiffness in the transversal direction and prevent undesired local deformations in the wing-box skin. Another consideration is the appearance of sources of instabilities such as buckling that require the inclusion of artificial damping factor into the simulation. 

Nonlinear simulations are carried out using this model and incorporating artificial energy dissipation through constant damping factor. The onset of the buckling phenomena and its evolution in the chiral lattice is characterized next. Results show that the collapse of the structure occurs when severe buckling appears on the ligaments of the chiral elements located at the root of the wing-box. This event produces a sudden reduction on the torsional stiffness of the structure and an increase in the wing-box twist adaptation observed at the tip. A second and more generalized buckling in the chiral lattice is observed to origin a second modification of the torsional stiffness for certain cases. In the baseline configuration, the length of the wing-box is 0.743 m, the width is 0.3 m and the height is 0.383 m. The load condition is a single point load applied on the upper flange of the tip rib and in the middle point of the width. For this case, the twist morphing of the wing-box is obtained to be equal to -1.25 degrees for the nonlinear simulation while the predicted twist for the linear simulation is -0.19 degrees.

Furthermore, a parametric study is performed on the computational model of the wing-box. Results show that considerable tailorability can be achieved through modifications of selected parameters. The parameter that displays a bigger influence in the onset and evolution of the elastic instabilities is the wing-box thickness. Increasing the wing-box thickness by 0.1 mm, provokes that the required force to induce the appearance of buckling at the root increases by 100 N. 

A wing model featuring a compliant spar design with the lattice of chiral elements is introduced to test the feasibility of the proposed concept under realistic aerodynamic loads. A weakly coupled aeroelastic analysis is performed with this model. The particular simulation case considers a wing with span equal 3 m, chord length equal to 0.5 m and air velocity of 30 m/s. The achieved twist deformation for this case was of about 4 degrees at the wing tip. Results from the simulations show that the wing twist adaptation increases as the air velocity increases. A single case was considered and, for it, the nonlinear and linear simulations displayed similar results. The developed model is fully parameterized and enables multiple parameter variations that would make it possible to achieve a more suitable wing configuration.  

In further studies of this technology, it would be necessary to numerically analyse the wing root bending moment variation after the mechanism activation and also manufacture a demonstrator that could be used to experimentally test the feasibility of the proposed concept. The analysis of the time-bounded response of this mechanism is beyond the scope of this preliminary work, but such a investigation would be a crucial prior implementation of the system on a real lift generating structure.

The proposed morphing has been shown to be capable of inducing global twist morphing of a wing-box exploiting local elastic instabilities. It has shown to be promising to be applied on realistic wing structures for which the torsional response is dominated by the wing-box. Potential applications may include load alleviation purposes on lift-generating structures with high aspect ratio. 